---
title: "LC-MS pre-processing report"
author: "`r print(QCreportObject$projectInfo$author)`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document: default
---

```{r setup, include=FALSE}
require(knitr, quietly=TRUE)
#knitr::opts_chunk$set(echo = TRUE)
#opts_knit$set(root.dir = projectdir)
```

&nbsp;

&nbsp;

&nbsp;


## Data processing summary
```{r projectsetup, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", strip.white=TRUE}
print(kable(QCreportObject$projectHeader))
```

&nbsp;

&nbsp;

&nbsp;


**XCMS peak picking summary:**
```{r xset_sum, echo=FALSE, message=FALSE, warning=FALSE, comment=""}
print(kable(QCreportObject$peakPickingParams))
```
\newpage
```{r s1, echo=FALSE, message=TRUE, warning=FALSE, comment="", cache=FALSE, fig.width=7}
QCreportObject$plots$ticplot_1
```

`r figs("S1")`

\newpage
```{r s2, echo=FALSE, message=TRUE, warning=FALSE, comment="", cache=FALSE, fig.width=7}
print(QCreportObject$plots$ticplot_2)
```

`r figs("S2")`

\newpage
```{r s3, echo=FALSE, message=TRUE, warning=FALSE, comment="", cache=FALSE, fig.width=7}
print(QCreportObject$plots$ticplot_3)
```

`r figs("S3")`

\newpage
```{r s4, echo=FALSE, message=TRUE, warning=FALSE, comment="", cache=FALSE, fig.width=7}
print(QCreportObject$plots$ticplot_4)
```

`r figs("S4")`

\newpage
```{r size_vs_peak_count, echo=FALSE, message=TRUE, warning=FALSE, comment="", cache=FALSE, fig.width=7}
print(QCreportObject$plots$ticplot_5)
```

`r figs("size_vs_peaknr")`
&nbsp;

&nbsp;

`r tbls("S1")`

```{r t1, echo=FALSE, message=TRUE, warning=FALSE, comment="", cache=FALSE, fig.width=7}
kable (QCreportObject$tables$corrMatrix, digits=10)
```

\newpage
```{r S5, echo=FALSE, message=FALSE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=6, prompt=FALSE}
print (QCreportObject$plots$PCAallSamples)
```

`r figs("S5")`

```{r S6, echo=FALSE, message=FALSE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=6, prompt=FALSE}
if (!is.null(QCreportObject$QC_label)){
  print(QCreportObject$plots$PCAQCsamples)
}
```

`r figs("S6")`

\newpage
```{r S7, echo=FALSE, message=FALSE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=6, prompt=FALSE}
if (!is.null(QCreportObject$QC_label)){
  print (QCreportObject$plots$PCAQCleading)
}
```

`r figs("S7")`

\newpage
```{r S8, echo=FALSE, message=FALSE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=6, prompt=FALSE}
if (!is.null(QCreportObject$QC_label)){
  print (QCreportObject$plots$PCAallQCleading)
}
```

`r figs("S8")`

\newpage
<!-- RT stability -->
`r tbls("RT_RSD")`

```{r RT_RSD_table, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
#if (!is.null(QCreportObject$QC_label)){
  #pander::pandoc.table(QCreportObject$tables$RT_rsd, round=c(rep(2,6),0), style="rmarkdown")
  #xtable::xtable(QCreportObject$tables$RT_rsd, digits=c(0,rep(2,6),0))
  kable (QCreportObject$tables$RT_rsd, digits=2)
#}
```

&nbsp;
&nbsp;
`r tbls("RT_MAD")`

```{r RT_MAD_table, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment=""}
#if (!is.null(QCreportObject$QC_label)){
  kable (QCreportObject$tables$RT_mad, digits=2)
#}
```

```{r RT_MAD_plot, echo=FALSE, message=FALSE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=6, prompt=FALSE}
#if (!is.null(QCreportObject$QC_label)){
  print (QCreportObject$plots$MAD_rt)
#}
```

`r figs("RT_MAD")`

\newpage

`r tbls("peak_width")`

```{r RT_PW_median, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", strip.white=TRUE}
#if (!is.null(QCreportObject$QC_label)){
  kable (QCreportObject$tables$peak_width, digits=2)
#}
```

```{r RT_PW_plot_median, echo=FALSE, message=FALSE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=6, prompt=FALSE}
#if (!is.null(QCreportObject$QC_label)){
  print(QCreportObject$plots$peak_width)
  #gridExtra::grid.arrange(ncol=1, QCreportObject$plots$peak_width_all, QCreportObject$plots$peak_width)
#}
```

`r figs("peak_width")`

\newpage
```{r EICs, echo=FALSE, message=TRUE, warning=FALSE, comment="", cache=FALSE, fig.width=7, fig.height=6}
if (!is.null(QCreportObject$plots$EICs)){
  QCreportObject$plots$EICs[[2]] <- QCreportObject$plots$EICs[[2]] + theme(legend.position = "none")
  QCreportObject$plots$EICs[[3]] <- QCreportObject$plots$EICs[[3]] + theme(legend.position = "none")
  grid.arrange (grobs=QCreportObject$plots$EICs, layout_matrix=matrix(c(1,2,1,3), nrow=2, ncol=2))
}
```

`r figs("S9")`

\newpage

`r tbls("mz_precision")`

```{r mz_ppm, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", strip.white=TRUE}
#if (!is.null(QCreportObject$QC_label)){
  kable (QCreportObject$tables$mz_median, digits=2)
#}
```

```{r mz, echo=FALSE, message=FALSE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=6, prompt=FALSE}
#if (!is.null(QCreportObject$QC_label)){
  #gridExtra::grid.arrange(ncol=1, QCreportObject$plots$mz_all, QCreportObject$plots$mz_median)
  print (QCreportObject$plots$mz_median)
#}
```

`r figs("mz_precision")`

\newpage
```{r missing_values, echo=FALSE, fig.height=6, fig.width=7, message=FALSE, warning=FALSE, cache=FALSE, comment="", results='hide'}
grid.arrange(QCreportObject$plots$MVplot1, QCreportObject$plots$MVplot2,                                          QCreportObject$plots$MVplot3,   QCreportObject$plots$MVplot4, 
             ncol=2, nrow=2)
```

`r figs("S10")`

\newpage
```{r S11, echo=FALSE, message=TRUE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=6}
print(QCreportObject$plots$RSDplot1)
```

`r figs("S11")`
&nbsp;

&nbsp;

`r tbls("S2")`

```{r T2, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", strip.white=TRUE}
kable (QCreportObject$tables$RSDtable1, digits=1)
```

\newpage
```{r rsd_values_3, echo=FALSE, message=TRUE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=6}
print (QCreportObject$plots$RSDplot2)
```

`r figs("S12")`

\newpage
```{r S13, echo=FALSE, message=FALSE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=9}
if (!is.null(QCreportObject$QC_label)){
  print (QCreportObject$plots$QCplot1)
}
```

`r figs("S13")`

\newpage
```{r S14, echo=FALSE, message=FALSE, warning=FALSE, comment="", cache=FALSE, results='hide', fig.width=7, fig.height=9}
if (!is.null(QCreportObject$QC_label)){
  print (QCreportObject$plots$QCplot2)
}
```

`r figs("S14")`

\newpage
<!-- Peak matrix filtering and S/B correction -->

`r tbls("filtering")`

```{r Peak matrix filtering, echo=FALSE}
if (!is.null(QCreportObject$QC_label)){
  kable (QCreportObject$filtering$table, digits=1)
}
```

List of samples removed by missing value filter:
```{r Samples removed, echo=FALSE}
if (!is.null(QCreportObject$QC_label)){
  print(QCreportObject$filtering$samples_removed)
}
```

Optimised glog lamba values:
```{r glog lambda, echo=FALSE}
if (!is.null(QCreportObject$QC_label)){
  kable(data.frame(data=c("Filttred", "Filtered, S/B corrected"), 
    "glog lambda"=c(QCreportObject$filtering$glog_lambda_filtered, 
      QCreportObject$filtering$glog_lambda_filtered_SB),
    check.names=FALSE))
}
```

\newpage
```{r SB_correction_2, echo=FALSE, fig.height=6, fig.width=7, message=TRUE, warning=FALSE, cache=FALSE, comment="", results='hide'}
if (!is.null(QCreportObject$QC_label)){ 
  print(QCreportObject$plots$SBPCAbefore)
}
if (!is.null(QCreportObject$plots$plots_per_batch_pca)){
  print(QCreportObject$plots$plots_per_batch_pca)
}
```

`r figs("S15")`

\newpage
```{r SB_correction_2a, echo=FALSE, fig.height=6, fig.width=7, message=TRUE, warning=FALSE, cache=FALSE, comment="", results='hide'}
if (!is.null(QCreportObject$QC_label)) {
  print(QCreportObject$plots$SBPCAbeforeQC)
}
```

`r figs("S16")`

\newpage
```{r SB_correction_3, echo=FALSE, fig.height=7, fig.width=7, message=TRUE, warning=FALSE, cache=FALSE, comment="", results='hide'}
if (!is.null(QCreportObject$QC_label)){
  print (QCreportObject$plots$SBPCAfter)
}
```

`r figs("S17")`

\newpage
```{r SB_correction_3a, echo=FALSE, fig.height=7, fig.width=7, message=TRUE, warning=FALSE, cache=FALSE, comment="", results='hide'}
if (!is.null(QCreportObject$QC_label)){
  print (QCreportObject$plots$SBPCAfterQC)
}
```

`r figs("S18")`

\newpage
```{r S19, echo=FALSE, fig.height=7, fig.width=7, message=TRUE, warning=FALSE, cache=FALSE, comment="", results='hide'}
if (!is.null(QCreportObject$QC_label)){
  print (QCreportObject$plots$SBRSDbefore)
}
```

`r figs("S19")`

\newpage
```{r S19a, echo=FALSE, fig.height=7, fig.width=7, message=TRUE, warning=FALSE, cache=FALSE, comment="", results='hide'}
if (!is.null(QCreportObject$plots$plots_per_batch_qc_rsd)){
  print (QCreportObject$plots$plots_per_batch_qc_rsd)
}
```

`r if (!is.null(QCreportObject$plots$plots_per_batch_qc_rsd)) figs ("S19a")`

\newpage
```{r S20, echo=FALSE, fig.height=7, fig.width=7, message=TRUE, warning=FALSE, cache=FALSE, comment="", results='hide'}
if (!is.null(QCreportObject$QC_label)){
  
  print (QCreportObject$plots$SBRSDafter)
}
```

`r figs("S20")`

\newpage
`r tbls("S3")`

```{r T3, echo=FALSE, fig.height=6, fig.width=7, message=TRUE, warning=FALSE, cache=FALSE, comment=""}
if (!is.null(QCreportObject$QC_label)){
  kable (QCreportObject$tables$SBtableBefore, digits=1)
}
```
&nbsp;

&nbsp;

`r tbls("S4")`

```{r T4, echo=FALSE, fig.height=6, fig.width=7, message=TRUE, warning=FALSE, cache=FALSE, comment=""}
if (!is.null(QCreportObject$QC_label)){
  kable (QCreportObject$tables$SBtableAfter, digits=1)
}
```

\newpage
`r tbls("S5")`
&nbsp;

```{r sampinfo_2, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, comment="", strip.white=TRUE}
kable (QCreportObject$samp.sum, catption="Summary of the sample metadata of the analytical batch")
```


